---
title: "SHP"
author: "Prabin Raj Shakya"
date: "August 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

## School Health Program 
The School Health Program screening app was developed in commcare for capturing the longitutinal data from school health program. The objective was to capture: 
1. School realted environmental and sanitaiton factors which will effect development of children 
2. Collect the individual children detailed personal data on the developemtn and factors feffecting the developlent. 

 
```{r}
shReg<-read.csv("~/R/SHP_V1/Data/SH_registration.csv")
shDetails<-read.csv("~/R/SHP_V1/Data/school_details.csv")
chReg<-read.csv("~/R/SHP_v1/Data/child_register.csv")
chStoolResults<-read.csv("~/R/SHP_v1/Data/stool_results.csv")
chDetail<-read.csv("~/R/SHP_v1/Data/school_child_que.csv")
waterResults<-read.csv("~/R/SHP_v1/Data/water_results.csv")
washMeasurement<-read.csv("~/R/SHP_v1/Data/")
```

## Data Sets Summary

The app generated following datasets: 
1. School Registration

```{r}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
